---
title: "STA100 Lab1"
author: "Po"
date: "4/6/2021"
output: html_document
---

```{r setup, include=FALSE}
options(width = 100)
knitr::opts_chunk$set(echo = TRUE)
```

# R and RStudio

Follow the below instructions to make yourself comfortable in using R/RStudio for statistical/scientific computing.

#### Scientific computing

- In **Console**, type and enter `1+1` and you will get
  ```{r}
  1+1
  ```

- Try `2.1*(3.7+4.9)/5.2`, `sin(pi/3)`, `exp(0.8)`, `log(1.0)` and anything. You can now throw away your TI-who-cares calculator!

#### Working directory

Working directory is the default folder in which files are saved and read.

- In the **Files** tab, find/create a folder for your STA100 work. Click **More** then **Set As Working Directory**.

- Download the `template.Rmd` in [Files/templates at STA100 Canvas site ](https://canvas.ucdavis.edu/courses/556874/files/folder/templates) and save it into your working directory. Then, open it by clicking on the `template.Rmd` showed in **Files** tab.

- **Knit** the `template.Rmd` into .pdf and .html respectively. The .pdf and .html file will appear alongside the `template.Rmd`.

#### R scripts

- Click the "little green plus icon" and select **R Script**. Then you obtain a notebook that for your to put R codes. Type some codes, for example
  ```{r}
  x <- 10.5
  y <- 8.1
  z <- x + y
  print(z)
  ```
  Click **Source** to and see the result `18.6` in **Console**.

- You can also **Run** line by line. Put your cursor to the line your want to run and click **Run**. You can also use hot-key **Command+Enter** in mac (or **Control+Enter** in Windows?).

- Click the floppy icon to save your R script in your working directory. Usually we save R scripts with file extension `.R`, for example, `the_best_script_ever.R`. Now you can shut down your computer and go out to enjoy the sunshine! See you all next week!

- Next week, open your script and work on it again.

#### Read data

R has many built-in functions to read data, for example, `read.table()`.

- Let's try to read the infamous [Fisher's Iris data set](https://en.wikipedia.org/wiki/Iris_flower_data_set).

- Go to the [UCI Machine Learning Repository page of Iris Data Set](https://archive.ics.uci.edu/ml/datasets/Iris). Click the link **Data Folder** and then download the two files `iris.data` and `iris.names`, and then save them into your working directory. T
  ```{r}
  lab2_data <- read.table("iris.data", sep = ",")
  ```
  Good job! You have load the data into R. Look the the **Environment** tab. You can see we have just created a variable named `lab2_data`. Click on it and peek what is inside!

- Ops, what are the columns `V1`, `V2`, `V3`, `V4` and `V5`? Open then text file `iris.names` and read the description! They are actually 
  ```
     1. sepal length in cm
     2. sepal width in cm
     3. petal length in cm
     4. petal width in cm
     5. class: 
        -- Iris Setosa
        -- Iris Versicolour
        -- Iris Virginica
  ```
  Rename the columns:
  ```{r}
  colnames(lab2_data) <- c("sepal_length", "sepal_width", "petal_length", "petal_width", "class")
  ```
  Check `lab2_data` again to see the change.
  
- Put the codes
  ```{r eval=FALSE}
  lab2_data <- read.table("iris.data", sep = ",")
  colnames(lab2_data) <- c("sepal_length", "sepal_width", "petal_length", "petal_width", "class")
  ```
  into your R script and save it! Now you can shut down your computer and go out to enjoy the sunshine! See you all next week!

#### Mean and standard deviation
  
- To access a column in a data frame, for example the `sepal_length` column in `lab2_data`, type `lab2_data$sepal_length` or `lab2_data["sepal_length"]`.

- Let's compute the mean and standard deviation of "sepal length" with functions `mean()` and `sd()`:
  ```{r }
  mean(lab2_data$sepal_length)
  ```
  ```{r }
  sd(lab2_data$sepal_length)
  ```

- R has lots of built-in functions for statistics. For example, the function `summary()` show you:
  ```{r}
  summary(lab2_data)
  ```
  
#### Histogram

- Let's plot a histogram.
  ```{r}
  hist(lab2_data$sepal_length,
       main = "Iris Data Set: Sepal Length in cm",
       xlab = "cm")
  ```

#### Help/Documentation

Read the R Documentation of the functions you learn today. Enter the following codes, one by one, and read the corresponding documentation/help in the **Help** tab.
```{r}
?sin
```
```{r}
?exp
```
```{r}
?log
```
```{r}
?read.table
```
```{r}
?colnames
```
```{r}
?mean
```
```{r}
?sd
```
```{r}
?summary
```
```{r}
?hist
```

How Po knows all those built-in functions in R?

- Way 1: Google it

- Way 2: Read R Help/Documentation

> Give a man a fish and you feed him for a day; Teach a man to fish and you feed him for a lifetime.

| Po        | Codes in labs | Google   | R Documentation |
|-----------|---------------|----------|-----------------|
| Fisherman | Fish          | Fish Rod | Sea             |
