---
title: "On the Ground"
author: "Roseanne Park | Match 2021"
abstract: |
  *I'm way up in the clouds and they say I've made it now, but I figured it out everything I need is on the ground.*
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=0.75in
header-includes:
  - \usepackage{verbatim,graphicx}
  - \usepackage{booktabs}
  - \renewcommand{\abstractname}{}
---

```{r setup, include=FALSE}
options(width=80)
knitr::opts_chunk$set(comment=NA, echo = FALSE)
pagebreak <- function() {
  if(knitr::is_latex_output()){return("\\newpage")} else {return('<div style="page-break-before: always;" />')}
}
```

# Hey

- Knit this Rmd file to see if you can make a html, pdf or words. You should be able to get a document. If you couldn't, just use RStudio Cloud or the Binder RStudio in the lab note homepage. Po likes RStudio. Everything you need is on the Cloud.

- Click the lovely green triangle button to run the chunks. Read the codes. Read the output. Understand the codes. Understand the data. 

- Sometime, the order of run is important. The most obvious example: you need to load the data and create the variables the for data before doing anything else.

- Edit, add, delete the codes as you need. Things here are just examples.

- Delete and insert words/writings as you need


`r pagebreak()`

# Codes in `LabAssignment2.Rmd`

## Data things

```{r}
# Load the data
vars <- c("ID","CHD","CAT","AGE","CHL","SMK","ECG","DBP","SBP","HPT","CH","CC")
evans <- read.table("http://www.stat.ucdavis.edu/~affarris/evans.dat",
                    header=FALSE,
                    col.names=vars)
```

The first 10 lines of the Evans data:
```{r}
# Print first 10 lines of the data
head(evans, 10)
```

Just let you know we can always put cool words everywhere.

## Age things

```{r}
# Min, Max, Mean, Median, Quantile of AGE
summary(evans$AGE)
```

We set `echo=TRUE` to show off a chunk of R codes.
```{r, echo=TRUE}
# Mean and SD
mean(evans$AGE)
sd(evans$AGE)
```

Here is a fancy way to put numbers into sentences: The mean of age is `r mean(evans$AGE)`. The sd of age is `r sd(evans$AGE)`.

```{r}
# Histogram of AGE
par(col="red")
hist(evans$AGE, main = "Histogram of Age", col = "#f4a7bb")
```

## Contingency Table things

```{r}
#contingency table of CAT vs CHD
CatChdTable <- table("High catecholamine level"=evans$CAT,
                 "Coronary heart disease"=evans$CHD)
CatChdTable
```

```{r}
# mosaic plot of CAT vs CHD
mosaicplot(CatChdTable,
           main="Mosaic plot of CAT vs. CHD",
           col = "#f4a7bb")
```

## Plot CHL things

```{r}
# Mean of CHL
aggregate(CHL~CHD+CAT,
          data=evans,
          mean)
```

```{r}
# SD of CHL
aggregate(CHL~CHD+CAT,
          data=evans,
          sd)
```

```{r}
# box plot of CHL in groups
boxplot(CHL~CHD+CAT,
        data=evans,
        xlab="CHD.CAT",
        names=c("Jisoo","Jennie","Rosé","Lisa"), 
        col="#f4a7bb")
```

```{r fig.height = 8, fig.width = 8, fig.align = "center"}
par(mfrow=c(2,2))

hist(evans$CHL[evans$CHD==0 & evans$CAT==0], 
     breaks = seq(min(evans$CHL)-5, max(evans$CHL)+5, length.out = 20),
     xlab = "CHL", 
     ylab = "Frequency", 
     main = "Histogram for CHL with CHD=0 and CAT=0",
     col = "#f4a7bb")

hist(evans$CHL[evans$CHD==0 & evans$CAT==1], 
     breaks = seq(min(evans$CHL)-5, max(evans$CHL)+5, length.out = 20),
     xlab = "CHL", 
     ylab = "Frequency", 
     main = "Histogram for CHL with CHD=0 and CAT=1",
     col = "#f4a7bb")

hist(evans$CHL[evans$CHD==1 & evans$CAT==0], 
     breaks = seq(min(evans$CHL)-5, max(evans$CHL)+5, length.out = 20),
     xlab = "CHL", 
     ylab = "Frequency", 
     main = "Histogram for CHL with CHD=1 and CAT=0",
     col = "#f4a7bb")

hist(evans$CHL[evans$CHD==1 & evans$CAT==1], 
     breaks = seq(min(evans$CHL)-5, max(evans$CHL)+5, length.out = 20),
     xlab = "CHL", 
     ylab = "Frequency", 
     main = "Histogram for CHL with CHD=1 and CAT=1",
     col = "#f4a7bb")
```

Just let you know we can make a list like that:

- Jisoo

- Jennie

- Rosé

- Lisa

or a list like that

1. How You Like That

2. Ice Cream

3. Pretty Savage

4. Bet You Wanna

5. Lovesick Girls

6. Crazy Over You

7. Love to Hate Me

8. You Never Know


`r pagebreak()`

# Fish

```{r}
SmkChdTable <- table("Smoking"=evans$SMK,
                     "Coronary heart disease"=evans$CHD)
SmkChdTable
```

```{r}
mosaicplot(SmkChdTable,
           main="Mosaic plot of SMK vs. CHD",
           col = "#f4a7bb")
```

```{r}
quantile_age = do.call(data.frame, aggregate(AGE~CHD+SMK,
          data=evans,
          quantile))
quantile_age
```

```{r}
boxplot(AGE~CHD+SMK,
        data=evans,
        xlab="CHD-SMK",
        sep = "-",
        main="Yo",
        col = "#f4a7bb"
        )
```

```{r}
# Surely Po does all the things to make the table pretty...
mean_sd_age = aggregate(AGE~CHD+SMK,
          data=evans,
          function(x) c(mean(x), sd(x)))
mean_sd_age=do.call(data.frame, mean_sd_age)
knitr::kable(mean_sd_age,
           format = "latex",
           booktabs = TRUE,
           longtable = FALSE,
           col.names = c("CHD", "SMK", "mean AGE", "SD AGE"),
           caption = "Mean and SD of age
           between the four groups obtained by heart disease and smoking status")
```



```{r fig.height = 8, fig.width = 8, fig.align = "center"}
par(mfrow=c(2,2))

hist(evans$AGE[evans$CHD==0 & evans$SMK==0], 
     breaks = seq(min(evans$AGE)-5, max(evans$AGE)+5, by=4),
     ylim = c(0, 80),
     xlab = "AGE", 
     ylab = "Frequency", 
     main = "Histogram for AGE with CHD=0 and SMK=0",
     col = "#f4a7bb")

hist(evans$AGE[evans$CHD==0 & evans$SMK==1], 
     breaks = seq(min(evans$AGE)-5, max(evans$AGE)+5, by=4),
     ylim = c(0, 80),
     xlab = "AGE", 
     ylab = "Frequency", 
     main = "Histogram for AGE with CHD=0 and SMK=1", 
     col = "#f4a7bb")

hist(evans$AGE[evans$CHD==1 & evans$SMK==0], 
     breaks = seq(min(evans$AGE)-5, max(evans$AGE)+5, by=4),
     ylim = c(0, 10),
     xlab = "AGE", 
     ylab = "Frequency", 
     main = "Histogram for AGE with CHD=1 and SMK=0",
     col = "#f4a7bb")

hist(evans$AGE[evans$CHD==1 & evans$SMK==1], 
     breaks = seq(min(evans$AGE)-5, max(evans$AGE)+5, by=4),
     ylim = c(0, 10),
     xlab = "AGE", 
     ylab = "Frequency", 
     main = "Histogram for AGE with CHD=1 and SMK=1", 
     col = "#f4a7bb")
```





`r pagebreak()`
# Appendix: R Script

```{r all-code, ref.label=setdiff(knitr::all_labels(), c("setup")), echo=TRUE, eval=FALSE}
```