---
title: "STA100 Lab3"
author: "Po"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
options(width = 100)
knitr::opts_chunk$set(echo = TRUE)
```

# Lab Assignment 1 (Lab projects?)

- Go though `LabAssignment1.pdf` [LabAssignment1.pdf](LabAssignment1.pdf)

- Open `LabAssignment1.Rmd` in RStudio and run codes!

- Open `template.Rmd` and save as a new .Rmd file for your Lab Assignment submission. Edit the author name, date and content. 

- Copy the codes in `LabAssignment1.Rmd` to your new .Rmd file and run the codes.

- Try to modify the codes according to the instruction in `LabAssignment1.pdf`. Run and see if you can get some numbers. Knit to see how the .pdf looks like.

- Tidy up the codes and writings. Knit and submit!

# R and RStudio continue

Follow the below instructions to make yourself comfortable in using R/RStudio for statistical/scientific computing.

### Working directory

Working directory is the default folder in which files are saved and read.

- In the **Files** tab, find/create a folder for your STA100 work. Click **More** then **Set As Working Directory**.

- Open the R script you worked on last week. Run the codes.

- Working directory is not persistent after you you close the R/RStudio. Remember to set working directory each time you open a R/RStudio.

### Read data

R has many built-in functions to read data, for example, `read.table()`.

- Let's try to read the infamous [Fisher's Iris data set](https://en.wikipedia.org/wiki/Iris_flower_data_set).

- Go to the [UCI Machine Learning Repository page of Iris Data Set](https://archive.ics.uci.edu/ml/datasets/Iris). Click the link **Data Folder** and then download the two files `iris.data` and `iris.names`, and then save them into your working directory. T
```{r}
lab2_data <- read.table("iris.data", sep = ",")
```
  Good job! You have load the data into R. Look the the **Environment** tab. You can see we have just created a variable named `lab2_data`. Click on it and peek what is inside!

- Ops, what are the columns `V1`, `V2`, `V3`, `V4` and `V5`? Open then text file `iris.names` and read the description! They are actually 
  ```
     1. sepal length in cm
     2. sepal width in cm
     3. petal length in cm
     4. petal width in cm
     5. class: 
        -- Iris Setosa
        -- Iris Versicolour
        -- Iris Virginica
  ```
  Rename the columns:
```{r}
colnames(lab2_data) <- c("sepal_length", "sepal_width", "petal_length", "petal_width", "class")
```
  Check `lab2_data` again to see the change.
  
- Put the codes
```{r eval=FALSE}
lab2_data <- read.table("iris.data", sep = ",")
colnames(lab2_data) <- c("sepal_length", "sepal_width", "petal_length", "petal_width", "class")
```
  into your R script and save it! Now you can shut down your computer and go out to enjoy the sunshine! See you all next week!

### Let's do some statistics!
  
- To access a column in a data frame, for example the `sepal_length` column in `lab2_data`, type `lab2_data$sepal_length` or `lab2_data["sepal_length"]`.

- R has lots of built-in functions for statistics. For example, the function `summary()` show you:
  ```{r}
  summary(lab2_data)
  ```

- Let's compute the mean and standard deviation of "sepal length" with functions `median`, `mean()` and `sd()`:
  ```{r }
  median(lab2_data$sepal_length)
  ```
  ```{r }
  mean(lab2_data$sepal_length)
  ```
  ```{r }
  sd(lab2_data$sepal_length)
  ```

- Let's plot a histogram.
```{r}
hist(lab2_data$sepal_length,
     main = "Iris Data Set: Sepal Length in cm",
     xlab = "cm")
```

- Let's standardize the sepal length
```{r fig.height=8}
mu <- mean(lab2_data$sepal_length)
sigma <- sd(lab2_data$sepal_length)
standardized_sepal_length <- (lab2_data$sepal_length - mu)/sigma

par(mfrow=c(2,1))
hist(lab2_data$sepal_length,
     breaks = seq(mu-3*sigma, mu+3*sigma,length.out=13),
     main = "Iris Data Set: Sepal Length in cm",
     xlab = "cm")
hist(standardized_sepal_length,
     breaks = seq(-3, 3, length.out=13),
     main = "Iris Data Set: Sepal Length standardized",
     xlab = "Sepal Length standardized")
```

### Simulations/Sampling

- Let's draw a sample of random numbers which follows normal distribution with mean `2.5` and standard deviation `1.2`
  ```{r}
  n <- 1000
  x <- rnorm(n, mean = 2.5, sd = 1.2)
  ```
  
  ```{r}
  hist(x)
  ```
  
  ```{r}
  mean(x)
  ```
  
  ```{r}
  sd(x)
  ```


- Let's draw random samples from BTS
  
  ![](https://upload.wikimedia.org/wikipedia/commons/thumb/0/0d/%E2%80%98LG_Q7_BTS_%EC%97%90%EB%94%94%EC%85%98%E2%80%99_%EC%98%88%EC%95%BD_%ED%8C%90%EB%A7%A4_%EC%8B%9C%EC%9E%91_%2842773472410%29_%28cropped%29.jpg/452px-%E2%80%98LG_Q7_BTS_%EC%97%90%EB%94%94%EC%85%98%E2%80%99_%EC%98%88%EC%95%BD_%ED%8C%90%EB%A7%A4_%EC%8B%9C%EC%9E%91_%2842773472410%29_%28cropped%29.jpg){width=15%}
  ```{r}
  bts <- c("Jin", "Suga", "J-Hope", "RM", "Jimin", "V", "Jungkook")
  ```
  What is the size of `bts`?
  ```{r}
  length(bts)
  ```
  
  Sampling!
  ```{r}
  subgroup_a <- sample(bts, 4, replace = FALSE)
  subgroup_b <- sample(bts, 4, replace = FALSE)
  ```
  
  ```{r}
  subgroup_a
  ```
  
  ```{r}
  subgroup_b
  ```
  
  What are the union and intersection of the subgroups?
  ```{r}
  union(subgroup_a, subgroup_b)
  intersect(subgroup_a, subgroup_b)
  ```
  
  | Set                     | Elements                              | Size                      |
  |-------------------------|---------------------------------------|---------------------------|
  | BTS (Population)        | `r bts`                               |`r length(bts)`            |
  | Subgroup A (Sample)     | `r subgroup_a`                        |`r length(subgroup_a)`     |
  | Subgroup B (Sample)     | `r subgroup_b`                        |`r length(subgroup_b)`     |
  | A or B (Union)          | `r union(subgroup_a, subgroup_b)`     |`r length(union(subgroup_a, subgroup_b))`     |
  | A and B (Intersect)     | `r intersect(subgroup_a, subgroup_b)` |`r length(intersect(subgroup_a, subgroup_b))`     |

### Help/Documentation

Read the R Documentation of the functions you learn today. Enter the following codes, one by one, and read the corresponding documentation/help in the **Help** tab.
```{r}
?read.table
```
```{r}
?colnames
```
```{r}
?summary
```
```{r}
?median
```
```{r}
?mean
```
```{r}
?sd
```
```{r}
?hist
```
```{r}
?par
```
```{r}
?rnorm
```
```{r}
?length
```
```{r}
?sample
```
```{r}
?union
```
```{r}
?intersect
```
How Po knows all those built-in functions in R?

- Way 1: Google it

- Way 2: Read R Help/Documentation

> Give a man a fish and you feed him for a day; Teach a man to fish and you feed him for a lifetime.

| Po        | Codes in labs | Google   | R Documentation |
|-----------|---------------|----------|-----------------|
| Fisherman | Fish          | Fish Rod | Sea             |

#### More R tutorial

- Interactive R course lessons **swirl** https://swirlstats.com/students.html

  Install **swirl** with the following commands.
  ```{r eval=FALSE}
  # If you haven't installed the swirl package yet
  install.packages("swirl")
  library(swirl)
  install_course_github("swirldev", "R_Programming_E")
  ```

  After **swirl** is installed (you only need to do it once), you can start/resume the R tutorial with the commands:
  ```{r eval=FALSE}
  library(swirl)
  swirl()
  ```
  Schedule some time to go though all the lessons by yourself! Almost all of the R codes you need to know are here in those lessons.

- If you prefer more static readings (Po did read them to learn R!):
  - R for Beginners https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf
  - An Introduction to R https://cran.r-project.org/doc/manuals/r-release/R-intro.pdf

- If you like RStudio's data science things,
  - R for Data Science https://r4ds.had.co.nz/
  - RStudio Primer https://rstudio.cloud/learn/primers/
