---
title: "STA100 Lab5"
author: "Po"
date: "4/27/2021"
output: html_document
---

```{r setup, include=FALSE}
options(width = 100)
knitr::opts_chunk$set(echo = TRUE)
```

# R tutorials that help you survive in the sea

- Interactive R course lessons **swirl** https://swirlstats.com/students.html

  Install **swirl** with the following commands.
  ```{r eval=FALSE}
  # If you haven't installed the swirl package yet
  install.packages("swirl")
  library(swirl)
  install_course_github("swirldev", "R_Programming_E")
  ```

  After **swirl** is installed (you only need to do it once), you can start/resume the R tutorial with the commands:
  ```{r eval=FALSE}
  library(swirl)
  swirl()
  ```
  Schedule some time to go though all the lessons by yourself! Almost all of the R codes you need to know are here in those lessons.

- If you prefer more static readings (Po did read them to learn R!):
  - R for Beginners https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf
  - An Introduction to R https://cran.r-project.org/doc/manuals/r-release/R-intro.pdf

- If you like RStudio's data science things,
  - R for Data Science https://r4ds.had.co.nz/
  - RStudio Primer https://rstudio.cloud/learn/primers/
