---
title: "STA100 Lab7"
author: "Po"
date: "6/11/2021"
output: html_document
---

```{r setup, include=FALSE}
require(pander)
options(width = 100)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE )
```

# Lab Assignment 4 (Lab projects?)

1. Go though `LabAssignment4.pdf` [LabAssignment4.pdf](LabAssignment4.pdf)

2. Download `LabAssignment4.Rmd` [LabAssignment4.Rmd](LabAssignment4.Rmd) [Me](LabAssignment4.Rmd) [MendelFigure1.png](MendelFigure1.png) [MendelFigure2.png](MendelFigure2.png)  in RStudio and run codes inside. Things should be exactly same as `LabAssignment4.pdf`.

3. Download, open `LabAssignment4_rev.Rmd` [LabAssignment4_rev.Rmd](LabAssignment3_jp.Rmd) and save as a new Rmd file for your own Lab Assignment submission. Knit this Rmd file to see if you can make a html, pdf or words. If you couldn't, just use RStudio Cloud or the Binder RStudio [![Binder](http://mybinder.org/badge_logo.svg)](http://mybinder.org/v2/gh/ucdavis-sta-100-spring-2021/polabs/main?urlpath=rstudio) set by Po.

4. Run/add/edit/delete the codes in your own copy of `LabAssignment4_rev.Rmd` and add/edit/delete some writings. Knit to see how the .pdf looks like. Tidy up the codes and writings. Knit and submit!

Pearson's chi-squared test

https://en.wikipedia.org/wiki/Pearson%27s_chi-squared_test

Hardcoding in `LabAssignment4.pdf`
```{r echo=TRUE}
NullRatio <- c(1,1,1,1,2,2,2,2,4)
NullProportion <- NullRatio/sum(NullRatio) # converting ratios to proportions
Observed <- c(38,35,28,30,65,68,60,67,138) # from Mendel's table
Expected <-sum(Observed)*NullProportion # converting proportions to Expected counts
Discrepancy <- (Expected-Observed)^2/Expected
TestStat <- sum(Discrepancy) # chi-squared test statistic
p_value <- 1-pchisq(TestStat,9-1) # don't forget the degrees of freedom!
pander(c(TestStat=TestStat, p_value=p_value))
```

Using R built-in function `chisq.test`
```{r echo=TRUE}
NullRatio <- c(1,1,1,1,2,2,2,2,4)
Observed <- c(38,35,28,30,65,68,60,67,138)
pander(chisq.test(Observed, p = NullRatio, rescale.p = TRUE))
```

# Help/Documentation

> There is no secret ingredient. 
> -- Mr. Ping `r emo::ji("noodle")`

Read the R Documentation of every functions you have seen.
```{r eval=FALSE}
?c
```
```{r eval=FALSE}
?rbind
```
```{r eval=FALSE}
?sum
```
```{r eval=FALSE}
?pchisq
```
```{r eval=FALSE}
?pander
```
```{r eval=FALSE}
?chisq.test
```
How Po knows all those built-in functions in R?

- Way 1: Google it

- Way 2: Read R Help/Documentation

# R tutorials that help you survive in Village `r emo::ji("mushroom")`

- Interactive R course lessons **swirl** https://swirlstats.com/students.html

  Install **swirl** with the following commands.
  ```{r eval=FALSE}
  # If you haven't installed the swirl package yet
  install.packages("swirl")
  library(swirl)
  install_course_github("swirldev", "R_Programming_E")
  ```

  After **swirl** is installed (you only need to do it once), you can start/resume the R tutorial with the commands:
  ```{r eval=FALSE}
  library(swirl)
  swirl()
  ```
  Schedule some time to go though all the lessons by yourself! Almost all of the R codes you need to know are here in those lessons.

- If you prefer more static readings (Po did read them to learn R!):
  - R for Beginners https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf
  - An Introduction to R https://cran.r-project.org/doc/manuals/r-release/R-intro.pdf

- If you like RStudio's data science things,
  - R for Data Science https://r4ds.had.co.nz/
  - RStudio Primer https://rstudio.cloud/learn/primers/

