---
title: "Jade Palace"
author: "Oogway |  January 2016"
abstract: |
  *Your mind is like this water my friend, when it is agitated it becomes difficult to see. But if you allow it to settle, the answer becomes clear.*
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=0.75in
header-includes:
  - \usepackage{verbatim,graphicx}
  - \usepackage{booktabs}
  - \renewcommand{\abstractname}{}
---

```{r setup, include=FALSE}
options(width=80)
knitr::opts_chunk$set(comment=NA, echo = FALSE)
pagebreak <- function() {
  if(knitr::is_latex_output()){return("\\newpage")} else {return('<div style="page-break-before: always;" />')}
}
```

# Hey

- Knit this Rmd file to see if you can make a html or pdf. If you couldn't, just use RStudio Cloud or the Binder RStudio in the lab note homepage. Po loves RStudio. Everything you need is on the Cloud.

- Edit, add, delete the codes as you need. Delete and insert words/writings as you need.

`r pagebreak()`

# Codes in `LabAssignment3.Rmd`

```{r}
hyperLik <- function(N,M,n,m){dhyper(m,M,N-M,n)}
```

```{r}
hyperLik(50, 10, 20, 4)
```

```{r}
hyperLik(100, 10, 20, 4)
```

```{r}
possibleN <- 26:50
likelihoods <- hyperLik(possibleN,10,20,4)
plot(possibleN,likelihoods,
     type="l", # linear interpolation for a smooth curve
     ylab="Likelihood",
     xlab="Possible population size")
```

```{r}
possibleN <- 26:150
likelihoods <- hyperLik(possibleN,10,20,4)
plot(possibleN,likelihoods,
     type="l", 
     ylab="Likelihood",
     xlab="Possible population size")
```

```{r}
est <- possibleN[which.max(likelihoods)]
est
```

# Panda Village example

```{r}
possibleN <- 20:50
likelihoods <- hyperLik(possibleN, 10, 15, 5)
plot(possibleN,likelihoods,
     type="l", 
     ylab="Likelihood",
     xlab="Possible population size")
```

```{r}
est <- possibleN[which.max(likelihoods)]
```

Based on maximum likelihood estimation, we estimate that the population size of pandas in Panda Village is `r est`.


`r pagebreak()`
# Appendix: R Script

```{r all-code, ref.label=setdiff(knitr::all_labels(), c("setup")), echo=TRUE, eval=FALSE}
```