---
title: "Butter"
author: "RM | May 2021"
abstract: |
  *I'm the nice guy.*
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=0.75in
header-includes:
  - \usepackage{booktabs}
  - \renewcommand{\abstractname}{}
---

```{r setup, include=FALSE}
options(width=80)
knitr::opts_chunk$set(comment=NA, echo = FALSE)
pagebreak <- function() {
  if(knitr::is_latex_output()){return("\\newpage")} else {return('<div style="page-break-before: always;" />')}
}
```

# Hey

- Knit this Rmd file to see if you can make a html or pdf. If you couldn't, just use RStudio Cloud or the Binder RStudio in the lab note homepage. Po loves RStudio. Everything you need is on the Cloud.

- Edit, add, delete the codes as you need. Delete and insert words/writings as you need.

`r pagebreak()`

# Codes in `LabAssignment6.Rmd`

## Part 1

Load data and peek.
```{r echo=TRUE}
#### Part I
ec <- read.csv("egyptianCotton.csv")
head(ec)
```

Fit ANOVA model
```{r echo=TRUE}
fittedModel <- aov(Luminance ~ Variety, 
                   data = ec
                   )
```

Model diagnostic 
```{r echo=TRUE}
par(mfrow=c(1,2)) ## two side-by-side plots
boxplot(Luminance ~ Variety, 
        data = ec,
        xlab="",
        las = 2, ## vertical labels
        col = "#F8DC4A"
        )
hist(fittedModel$residuals,
     ylab="Frequency",
     xlab="Residual",
     main="",
     col = "#F8DC4A"
     )
normalData <- rnorm(dim(ec)[1])
resids <- aov(normalData~Variety, data=ec)$residuals
hist(resids, col = "#F8DC4A")
```

Compute/show cool statistics things
```{r echo=TRUE}
anova(fittedModel)
tuky <- TukeyHSD(fittedModel, 
                 conf.level = 0.99
                 )
par(mar=c(5,6,4,1)+1.2) ## so that labels don't get cut off
plot(tuky, 
     las=1 ## horizontal labels
     )
```

`r pagebreak()`

## Part II

Data is [\textcolor{blue}{AnesthesiaVentilation.csv}](http://www.stat.ucdavis.edu/~affarris/AnesthesiaVentilation.csv)

```{r echo=TRUE}
av <- read.csv("AnesthesiaVentilation.csv")
# Or read.csv("http://www.stat.ucdavis.edu/~affarris/AnesthesiaVentilation.csv")
head(av, 10)
```
```{r echo=TRUE}
boxplot(folate ~ ventilation, 
        data = av,
        main = "Po is a nice guy.",
        col = "#F8DC4A"
        )
```

```{r echo=TRUE}
fittedModel <- aov(folate ~ ventilation, 
                   data = av
                   )
anova(fittedModel)
```

```{r echo=TRUE}
tuky <- TukeyHSD(fittedModel, 
                 conf.level = 0.99
                 )
par(mar=c(5,12,4,2)+0.1)
plot(tuky, 
     las=1 ## horizontal labels
     )
```


`r pagebreak()`
# Appendix: R Script

```{r all-code, ref.label=setdiff(knitr::all_labels(), c("setup")), echo=TRUE, eval=FALSE}
```