---
title: "Lady Tasting Tea"
author: "Muriel Bristol | April 1888"
abstract: |
  *Cause we're living boba life*
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=0.75in
header-includes:
  - \usepackage{booktabs}
  - \renewcommand{\abstractname}{}
---

```{r setup, include=FALSE}
options(width=80)
knitr::opts_chunk$set(comment=NA, echo = FALSE)
pagebreak <- function() {
  if(knitr::is_latex_output()){return("\\newpage")} else {return('<div style="page-break-before: always;" />')}
}
```

# Hey

- Knit this Rmd file to see if you can make a html or pdf. If you couldn't, just use RStudio Cloud or the Binder RStudio in the lab note homepage. Po loves RStudio. Everything you need is on the Cloud.

- Edit, add, delete the codes as you need. Delete and insert words/writings as you need.

`r pagebreak()`

# Codes in `LabAssignment5.Rmd`

## Part I

```{r echo=TRUE}
#### Part I
counts <- matrix(c(8,87,3,23),2,2)
rownames(counts) <- c("Asthma","No asthma")
colnames(counts) <- c("Resolved","Persistent")
pVal <- fisher.test(counts)$p.val
knitr::kable(counts)
```
Based on the data, the p-value of Fisher's exact test is `r round(pVal,4)`.

## Part II

```{r echo=TRUE}
### Part II
SeroprevalenceTable <- matrix(c(369,2,3280,50),2,2)
rownames(SeroprevalenceTable) <- c("Negative","Positive")
colnames(SeroprevalenceTable) <- c("Manufacturer", "Stanford")
knitr::kable(SeroprevalenceTable)
```


`r pagebreak()`
# Appendix: R Script

```{r all-code, ref.label=setdiff(knitr::all_labels(), c("setup")), echo=TRUE, eval=FALSE}
```