---
title: "On the Ground"
author: "Roseanne Park | Match 2021"
abstract: |
  *My life's been magic, seems fantastic. I used to have a hole in the wall with a mattress. Funny when you want it, suddenly you have it. You find out that your gold's just plastic.*
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=0.75in
header-includes:
  - \renewcommand{\abstractname}{}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, echo = FALSE)
pagebreak <- function() {
  if(knitr::is_latex_output()){return("\\newpage \\hrulefill")} else {return('<div style="page-break-before: always;" />')}
}
```

# Test sensitivity

```{r}
CheckOnce <- function(FullSequence,TestRef,readLength){
        # Randomly sample a location on the genome to read
        RandomIndex <- sample(1:(nchar(FullSequence) - readLength + 1),1)
        RandomSnippet <- substr(FullSequence, RandomIndex, RandomIndex + readLength - 1)
        # Check to see if it contains the ref. string
        grepl(TestRef,RandomSnippet) 
} 
Test <- function(FullSequence,TestRef,readLength,numReps){
        # Repeat the test numReps times;
        # if any find the reference, return +
        Reps <- replicate(numReps,CheckOnce(FullSequence,TestRef,readLength)) 
        ifelse(any(Reps),"+","-")
}
```

```{r}
SeqLines <- readLines("http://www.stat.ucdavis.edu/~affarris/CovidRef.txt")
CovSequence <- paste(SeqLines[-1], collapse="")
RefSubseq <- substr(CovSequence,27202,27387)
```

In a simulation with

- Reference subsequence the subsequence from nucleotide 27202 to 27387 of the MN908947.3 complete genome

- test sequences of length 3000

- 12 random reads

- 1000 replications of the test

we have the following result:
```{r}
repl1000 <- replicate(1000,Test(CovSequence,RefSubseq,3000,12))
results <- table(repl1000)
results
```

We would estimate that this test has a sensitivity of about $\frac{ `r results[2]` }{  `r results[1]` + `r results[2]` } \approx `r round(results[2]/(results[1] + results[2]),2)`$.

`r pagebreak()`
# Appendix: R Script

```{r all-code, ref.label=setdiff(knitr::all_labels(), c("setup")), echo=TRUE, eval=FALSE}
```